Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-05-07 ms.tex
plots showing PCA model and residuals.

@@

@@

We start by taking the average transit light curve of all the long cadence data (the mean of the 2D grid along the transit number axis).
We then take the dot product ($\bullet$) with this average light curve to create an amplitude time series.
\begin{equation}
A = \frac{(f - 1) \bullet a}{a \bullet a},
\end{equation}
where $A$ is the amplitude vector, $f$ is the flux matrix with x indices of time and y indices of transit number and $a$ is the average spectrum.
This dot product is then multiplied by the average transit light curve to create a 2D model grid.
The residual of this model shows substantial deviations from white noise, so we explore more sophisticated models than the average light curve.

@@

As another way of analyzing the light curve data, we apply Principal Component Analysis (PCA) to this two dimensional grid.
We start by rescaling the two dimensional grid to have zero mean and a variance of 1.0 along the Transit Number axis.
Next, we perform PCA on the two dimensional grid to identify eigenvectors as a function of orbital phase and then the principal components as a function of transit number.

@@

>>>>

\subsection{Kepler Secondary Eclipse}

@@

\subsection{PCA Analysis}

@@

We start by taking the average transit light curve of all the long cadence data (the mean of the 2D grid along the transit number axis).
We then take the dot product ($\bullet$) with this average light curve to create an amplitude time series.
\begin{equation}
A = \frac{(f - 1) \bullet a}{a \bullet a},
\end{equation}
where $A$ is the amplitude vector, $f$ is the flux matrix with x indices of time and y indices of transit number and $a$ is the average spectrum.
This dot product is then multiplied by the average transit light curve to create a 2D model grid.
The residual of this model shows substantial deviations from white noise, so we explore more sophisticated models than the average light curve below.

@@

As another way of analyzing the light curve data, we apply Principal Component Analysis (PCA) to this two dimensional grid.
We start by rescaling the two dimensional grid to have zero mean and a variance of 1.0 along the Transit Number axis, while saving the transformation to return to the original flux units.
This first rescaling step will remove the constants from the transit light curve (such as the planet candidate's transit curve).
Next, we perform PCA on the two dimensional grid to identify eigenvectors as a function of orbital phase and then the principal components as a function of transit number.

@@

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/photometry_riverplot.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/pca_model_2D.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/pca_resid_2D.pdf}
\caption{Cleaned Kepler Long-cadence data (Top Left) and model fit using 4 Principal Components (Top Right).
(Bottom) The residuals show smaller residuals than the average model.
}\label{fig:riverPlotsPCA}
\end{centering}
\end{figure*}
